Blum axioms and nondeterministic computation of functions

### 2016-04-19 paper.tex
paper.tex: Add section "Project Development".

\subsection{Hopcroft-Ullman's definition}

@@

\subsection{Proposed definition}

@@

\subsubsection{Extension $\NP$-completeness}

@@

>>>>

\subsection{Hopcroft-Ullman's definition}
\label{sec:hopcroft-ullman}

@@

\subsection{Proposed definition}
\label{sec:proposed}

@@

\subsubsection{Extension $\NP$-completeness}
\label{sec:np-completeness-extension}

@@

\section{Project Development}

Tiago Royer studied this problem of associating a nondeterministic machine
with a function in his undergraduate thesis\footnote{
    The project was developed while he was an undergraduate student
    at Federal University of Santa Catarina (UFSC).
    Currently, he is pursuing his master's degree
    at the University of São Paulo (USP).
},
under the supervision of Jerusa Marchi.
After finding Hopcroft and Ullman's definition
(section~\ref{sec:hopcroft-ullman})
and noting it yields a computation that is very close to be deterministic,
he devised the definition of section~\ref{sec:proposed}
(using the concept of acceptable Gödel numberings and Blum axioms
to be sure his definition would not bee too unreasonable).
As noted in section~\ref{sec:np-completeness-extension},
his generalization to $\NP$ and $\NP$-completeness are very rigid.

Krentel's and Valiant's definitions
(which were discovered later in the project),
although not created specifically to associate nondeterministic machine with functions,
provides a more elegant generalization of $\NP$ and $\NP$-completeness;
this paper summarize all these definitions
under the light of Gödel numberings and Blum axioms.
